Arc Blanc: a real time ocean simulation framework

### 2024-11-14 paper.tex
change term

In \framework, the number of IFFT applications is divided by two using Theorem \ref{theorem:ifft} on Hermitian matrices\footnote{A matrix $X=(x_{n,m})$ is Hermitian if it is equal to its own conjugate transpose: $X = X^{\dagger}$ or $x_{n,m}=x^*_{m,n}$.} (see annex \ref{sec:annexe-2IFFT} for its demonstration).
\begin{theorem}
	\label{theorem:ifft}
	Let: $X=(x_{n,m}), Y=(y_{n,m}) \in M_n(\mathbb{C})$ be two Hermitian matrices.
	Then the following relation is valid:
	\begin{equation}
		\mathcal{F}^{-1}\left(X+iY\right) =
		\Re\left(\mathcal{F}^{-1}\left(X\right)\right)
		+ i\Re\left(\mathcal{F}^{-1}\left(Y\right)\right)
	\end{equation}
\end{theorem}
Hence, in \framework the coefficients in frequency space of two Hermitian matrices $X$ and $Y$ are combined in a single matrix $H=X+iY$.
Using Theorem \ref{theorem:ifft}, one complex IFFT suffices to obtain the real parts of two IFFT $\mathcal{F}^{-1}\left(X\right)$ and $\mathcal{F}^{-1}\left(Y\right)$.
This treatment allows reducing IFFT computation times by a factor close to 2.

>>>>

In \framework, the number of IFFT applications is divided by two using Theorem \ref{theorem:ifft} on Hermitian matrices\footnote{A matrix $X=(x_{n,m})$ is Hermitian if it is equal to its own conjugate transpose: $X = X^{\dagger}$ or $x_{n,m}=x^*_{m,n}$.} (see annex \ref{sec:annexe-2IFFT} for its proof).
\begin{theorem}
	\label{theorem:ifft}
	Let: $X=(x_{n,m}), Y=(y_{n,m}) \in M_n(\mathbb{C})$ be two Hermitian matrices.
	Then the following relation is valid:
	\begin{equation}
		\mathcal{F}^{-1}\left(X+iY\right) =
		\Re\left(\mathcal{F}^{-1}\left(X\right)\right)
		+ i\Re\left(\mathcal{F}^{-1}\left(Y\right)\right)
	\end{equation}
\end{theorem}
Hence, in \framework the coefficients in frequency space of two Hermitian matrices $X$ and $Y$ are combined in a single matrix $H=X+iY$.
Using Theorem \ref{theorem:ifft}, one complex IFFT suffices to obtain the real parts of two IFFT $\mathcal{F}^{-1}\left(X\right)$ and $\mathcal{F}^{-1}\left(Y\right)$.
This treatment allows reducing IFFT computation times by a factor close to 2.
